\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

Agent:

This thesis presents the design and implementation of a multilingual document translation system
built for multinational enterprise environments. In organizations operating across multiple Asian
countries, technical documents must be translated accurately and consistently across many
languages, posing challenges in specialized terminology management, multi-format document
support, and scanned-document processing.

The system adopts a three-tier architecture: a Single-Page Application (SPA) frontend built with
React~18 and Vite~6, a REST~API layer powered by Django REST Framework~3.16, and a data layer
comprising PostgreSQL, AWS~S3, and Google Cloud Storage. The translation core integrates
Google Cloud Translation~API~v3 with 44 custom glossary pairs spanning 10~languages: Vietnamese,
Japanese, Simplified Chinese, Traditional Chinese, English, Thai, Bengali, Hindi, Indonesian,
and Oriya. Five document formats are supported: DOCX, XLSX, PPTX, PDF (including scanned
documents), and CSV/XLS.

Three key technical contributions are reported: (1)~a multi-format translation pipeline with
intelligent PDF classification, automatically routing native-text PDFs through a
ConvertAPI→DOCX path and scanned PDFs through an Azure Document Intelligence OCR pipeline;
(2)~a three-tier crowdsourced terminology management system with a threshold-based suggestion
queue, allowing users to contribute terms to the shared library through a voting mechanism;
(3)~a thread-local context injection mechanism that transparently supplies the selected glossary
mode (none / common / private) to all translation sub-modules without modifying their signatures.

The completed system is deployed on AWS infrastructure, leveraging Amazon Cognito SSO for
enterprise authentication and AWS Application Load Balancer for traffic distribution, serving
real-world multilingual technical-document translation needs in a production environment.

\bigskip
\noindent\textbf{Keywords:} machine translation, multilingual, terminology management, document
processing, OCR, Google Cloud Translation, Django REST Framework, React.
